\section*{Acknowledgements}
This master thesis would not have been possible without the help of countless of people around me, to some of whom I would like to show special gratitude. \\
%
First I wish to thank my girlfriend and family for supporting me and listening to my complains and allowing me to work long hours during the final phases of this work, who always supported me and helped in lightening my spirit during the thesis. 
I'd also like to thanks all family members and friends that helped me by proofreading and supporting me while writing this thesis.
I would not have come so far without the support and privilege of having this supportive people at my side.\\ \\
%
% Annette 
My deepest gratitude goes to my principle supervisor Prof.-Dr.~Annette Ladstätter-Weißenmayer, that sparked my interest in the topic of urban heat islands during the lecture \textit{Biogeochemistry} and introduced me to the cooperation project with OHB Digital Connect GmbH. 
She also help me in countless meetings with answers to my questions, interesting ideas and conversations and general support for the thesis as well as guidance and advocacy have profoundly impacted the successful completion of this work and my academic career.\\ \\
%
% Adrian 
Further I'd like to thank my secondary supervisor Dr.\ Adrian Fessel who helped me immensely with the development of the image processing pipeline and always had helpful suggestions and ideas on how to overcome problems and limitations when working on the processing software and deepen my understanding in machine learning and remote sensing. 
He always had helpful suggestions and supported my work in many different ways and gave many insightful guidances to how to handle all kinds of problems.\\ \\
%
% Daro 
I would also like to thank the nice people at OHB Digital GmbH especially Daro Krummrich that helped me with lots of organisational support and lots of very smart advice and support during the time of writing, he always had my back and my best interest in mind. He and all colleagues at OHB always had helpful tips and advice when I had any questions.
%
I'd also like to thank all the numerous scientists working in this field and dedicating whole careers on providing insides into our everyday live and environment. All the numerous sources I was able to use and base this work on. 
\newpage
